Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-19 paper.qmd
Updated Figure 5 with projection function

plot_proj <- function(projected_df, model_df, axes, circle, 
                      point_param = c(1.5, 0.5, "#000000"), # size, alpha, color
                      line_param = c(0.5, 0.5, "#000000"), #linewidth, alpha
                      plot_limits, title, cex = 2, 
                      axis_text_size = 3,
                      is_category = FALSE) {

@@

  initial_plot + 
    geom_segment(
      data = model_df, 
      aes(
        x = proj1_from, 
        y = proj2_from, 
        xend = proj1_to, 
        yend = proj2_to), 
      color = line_param[3],
      linewidth = as.numeric(line_param[1]),
      alpha = as.numeric(line_param[2])) +
    geom_point(
      size = as.numeric(point_param[1]),
      alpha = as.numeric(point_param[2]),
      color = point_param[3]) +
    geom_segment(
      data=axes, 
      aes(x=x1, y=y1, xend=x2, yend=y2), 
      colour="grey70") +
    geom_text(
      data=axes,
      aes(x=x2, y=y2), 
      label=rownames(axes),
      colour="grey50",
      size = axis_text_size) +
    geom_path(
      data=circle, 
      aes(x=c1, y=c2), colour="grey70") +
    xlim(plot_limits) +
    ylim(plot_limits) +
    interior_annotation(title, cex = cex)

@@

two_curvy_proj_tsne_first_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, 0.6)) + 
  ylim(c(-0.6, 0.6)) +
  interior_annotation("c", sc_ltr_pos, cex = 1.5) +
  theme(
    legend.position = "none"
  )

@@

two_curvy_proj_tsne_all_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = true_model_df_proj, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#2b8cbe") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, 0.6)) + 
  ylim(c(-0.6, 0.6)) +
  interior_annotation("d", sc_ltr_pos, cex = 1.5) +
  theme(
    legend.position = "none"
  )

>>>>

plot_proj <- function(projected_df, model_df, axes, circle, 
                      point_param = c(1.5, 0.5, "#000000"), # size, alpha, color
                      line_param = c(0.5, 0.5, "#000000"), #linewidth, alpha
                      plot_limits, title, cex = 2, 
                      position = c(0.92, 0.92), 
                      axis_text_size = 3,
                      is_category = FALSE) {

@@

  initial_plot <- initial_plot + 
    geom_segment(
      data = model_df, 
      aes(
        x = proj1_from, 
        y = proj2_from, 
        xend = proj1_to, 
        yend = proj2_to), 
      color = line_param[3],
      linewidth = as.numeric(line_param[1]),
      alpha = as.numeric(line_param[2])) +
    geom_point(
      size = as.numeric(point_param[1]),
      alpha = as.numeric(point_param[2]),
      color = point_param[3]) +
    geom_segment(
      data=axes, 
      aes(x=x1, y=y1, xend=x2, yend=y2), 
      colour="grey70") +
    geom_text(
      data=axes,
      aes(x=x2, y=y2), 
      label=rownames(axes),
      colour="grey50",
      size = axis_text_size) +
    geom_path(
      data=circle, 
      aes(x=c1, y=c2), colour="grey70") +
    xlim(plot_limits) +
    ylim(plot_limits) +
    interior_annotation(title, position, cex = cex)

  initial_plot

@@

two_curvy_proj_tsne_first_model1 <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(0.5, 0.2, "#636363"), # size, alpha, color
    line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
    plot_limits = c(-0.6, 0.6), 
    title = "c", 
    cex = 1.5, 
    position = sc_ltr_pos,
    axis_text_size = 4, 
    is_category = FALSE) +
    theme(
        legend.position = "none"
    )

@@

two_curvy_proj_tsne_all_model1 <- plot_proj(
  projected_df = projected_df, 
  model_df = true_model_df_proj, 
  axes = axes, 
  circle = circle, 
  point_param = c(0.5, 0.5, "#636363"), # size, alpha, color
  line_param = c(0.5, 0.5, "#2b8cbe"), # linewidth, alpha
  plot_limits = c(-0.6, 0.6), 
  title = "d", 
  cex = 1.5, 
  position = sc_ltr_pos,
  axis_text_size = 4, 
  is_category = FALSE) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000")
